Endogenous Politics and \\ the Design of Trade Institutions

### 2016-07-21 feedback.tex
add feedback from talks in 2014

\newpage
\section{Feedback on 2014 draft}
\subsection{May 30, 2014, Spring Midwest meetings}
\begin{itemize}
	\item Rick Bond, Ian Wooton, James Lake, Mostafa, David Kuenzel at the talk
	\item James: need to be more precise about when $\ga$ is evaluated
\end{itemize}

>>>>

\newpage
\section{Feedback on 2014 draft}
\subsection{May 30, 2014, Spring Midwest meetings}
\begin{itemize}
	\item Rick Bond, Ian Wooton, James Lake, Mostafa, David Kuenzel at the talk
	\item Rick: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
	\item James: need to be more precise about when $\ga$ is evaluated
		\begin{itemize}
			\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
		\end{itemize}
	\item Ex-ante lobbying: need to understand MRC07 result that tariff-cap = strong binding
\end{itemize}

\subsection{Sept. 12, 2014, ETSG}
\begin{itemize}
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\item Baldwin-style welfare function works for a set of questions, but not for this one
			\item GH is isomorphic
		\end{itemize}
	\item Coates Ludema 2001
		\begin{itemize}
			\item What if WTO actually \textit{did} what literature says it does? It wouldn't work!
			\item Be more explicit about the relationship between $\ga(e)$ and $\ga(s)$
		\end{itemize}
	\item I need to be able to say which questions are okay with
		\begin{enumerate}
			\item unweighted/standard welfare function
			\item $\ga(s)$ only (i.e. predictions/design predictions won't change lobbying incentives) 
		\end{enumerate}
\end{itemize}

\subsection{Oct. 17, 2014, McGill}
\begin{itemize}
	\item Hanson and Sargent, model uncertainty
	\item Why Nash bargain for tariff cap?
\end{itemize}

\subsection{Nov. 7, 2014, Ryerson}
\begin{itemize}
	\item Export lobby at ex-post b/c wants to reduce chance of trade war
	\item $e$ in terms of numeraire
	\item Could escape clause be made to work with some fancier set up, e.g. dynamic use constraint?
\end{itemize}
